Implementation of a lattice Boltzmann method for immiscible multiphase flow simulations using the level set method

### 2015-11-14 Paper/paper.tex
Paper in PDF Version

In this publication we use a hybrid lattice Boltzmann level set method. Thereby the interface motion is calculated by the level set method. The input data for the level set method is given by the lattice Boltzmann method, which is calculated independently for each fluid. This method has the advantage that it allows for big ranges of density and viscosity ratios between the fluid phases 
and has a high accuracy but requires only little memory %TODO das ist zu unscharf, glaube ich
.

@@

  \tilde{\rho}(x) = 3\rho(x+c_i,t+1) - 3\rho(x+2c_i,t+1) + \rho(x+3c_i,t+1).

@@

  \tilde{u}(x) = 3u(x+c_i,t+1) - 3u(x+2c_i,t+1) + u(x+3c_i,t+1).

>>>>

In this publication we use a hybrid lattice Boltzmann level set method. Thereby, the interface motion is calculated by the level set method. The input data for the level set method is given by the lattice Boltzmann method, which is calculated independently for each fluid. This method has the advantage that it allows big ranges of density and viscosity ratios between the fluid phases 
and has a high accuracy but requires only little memory %TODO das ist zu unscharf, glaube ich
.

@@

  \tilde{\rho}(x) = 3\rho(x+c_i,t) - 3\rho(x+2c_i,t) + \rho(x+3c_i,t).

@@

  \tilde{u}(x) = 3u(x+c_i,t) - 3u(x+2c_i,t) + u(x+3c_i,t).
